Using Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2020-12-09 thesis/thesis.tex
thesis: Add NGC 2632 results

Once data is available in TOPCAT, we have to carefully analyze the imported data.
From there, we can perform a first stars selection by excluding those stars with probability value lower than 0.8.
This first result can be taken as a good staring point, but we still need to make some fine tunning.
As we can see in Figure \ref{fig:topcat_prob_selection_melotte_22}, the selection is too restrictive and we have lost too much stars.

@@

Until now, we have focused our study in Melotte 22 OC. Since our main aim is to get a model that fits well for a wide range of clusters,
we present now the results obtained for a selection of clusters with different topologies.

>>>>

Once data is available in TOPCAT, we have to carefully analyze the imported data.
From there, we can perform a first stars selection by excluding those stars with probability value lower than 0.8.
This first result can be taken as a good staring point, but we still need to make some fine tunning.
As we can see in Figure \ref{fig:topcat_prob_selection_melotte_22}, the selection is too restrictive and we have lost too many stars.

@@

Until now, we have focused our study in the open cluster Melotte 22.
Since our aim is to get a model that fits well for a wide range of clusters,
we present now some results obtained for a selection of clusters with different topologies.

\subsection{NGC 2632}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 Clusterix+TOPCAT characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 KMeans characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 DEC characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_pm_filtered_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_filtered_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_filtered_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 DEC (filtered) characterization.}
\end{figure}

\begin{table}[H]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      \# Clusters & 10 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 10 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2632 DEC model hyperparameters.}
    \label{tab:hyperparameters_ngc_2632}
  \end{center}
\end{table}

\begin{table}[H]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \textbf{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \textbf{$\mu_{\delta}$ $(mas/yr^{-1})$} & \textbf{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -36.047 $\pm$ 0.110 & -12.917 $\pm$ 0.066 & 5.371 $\pm$ 0.003 & - \\
      Clusterix+TOPCAT & -36.154 $\pm$ 1.001 & -12.909 $\pm$ 0.806 & 5.327 $\pm$ 0.187 & 371 \\
      KMeans & -26.352 $\pm$ 20.562 & -15.828 $\pm$ 19.152 & 5.394 $\pm$ 0.696 & 629 \\
      DEC & -20.012 $\pm$ 20.657 & -14.742 $\pm$ 17.330 & 4.686 $\pm$ 0.855 & 894 \\
      \textbf{DEC (filtered)} & -21.571 $\pm$ 19.825 & -14.234 $\pm$ 16.388 & 4.719 $\pm$ 0.706 & 714 \\
    \end{tabular}
    \caption{NGC 2632 results.}
    \label{tab:results_ngc_2632}
  \end{center}
\end{table}
